\emph{Gaia} DR2 adds clues for dynamical ejection of a $\sim$$150\,M_\odot$ star

### 2018-06-06 VFTS682.tex
backup
changed figure and caption

While \emph{Gaia} DR2 data can be correlated, this is
not an issue for VFTS682, and we treat the proper motion components ($\mu_\mathrm{RA}$, and $\mu_\mathrm{DEC}$,
respectively) of the star as uncorrelated for simplicity.
% We retrieve for VFTS682 the position in RA and DEC
% in the International Celestial Reference System \cite[][]{brown:18},
% its
% proper motion components .
%  and for simplicity we treat them as
% uncorrelated in the following.
For the radial velocity of VFTS682 and of the 30 Doradus
region as a whole, we instead use the VFTS data
as quoted in \cite{bestenlehner:11}. \Tabref{tab:vfts682} lists the values adopted throughout
this work for each of these quantities.

@@

The red arrow in \Figref{fig:main} shows the direction of relative proper motion of
VFTS682 from \emph{Gaia} DR2 (see \Eqref{eq:pm_gaia_around}), and the
orange arrows illustrate the uncertainty. % show the possible
% range of directions within the uncertainties in the measured relative proper
% motion.
These arrows cross at the present-day location of VFTS682 and
are prolonged in the direction opposite to the motion to illustrate
the possible range of origins. % The green arrow shows the direction of
% the relative proper motion from HST (see \Eqref{eq:pm_around_HST}),
% but we omit to show the possible range of directions from HST data, since it is
% insufficiently constrained to be useful.

@@

\begin{figure}%[tbp]
  \centering
  \includegraphics[width=0.48\textwidth]{./figures/main_plot_good_gaia_only}  
  \caption{The red solid arrow indicates the proper motion of VFTS682
    relative to the region from \emph{Gaia} DR2, starting from the present day position of
    the star. The orange arrows indicate the possible
    directions of projected motion within the \emph{Gaia} DR2 errors, and are extended
    backwards (dashed) to illustrate the uncertainty on the origin of the
    star. The length of the prolongations is proportional to the relative proper motion
    times the kinetic age of VFTS682. % \todo{load color picture on background? Fig with HST data
      % available, but confusing...}
  }

>>>>

While \emph{Gaia} DR2 data can be correlated, this is
not an issue for VFTS682, and we treat the proper motion components ($\mu_\mathrm{RA}$, and $\mu_\mathrm{DEC}$,
respectively) of the star as uncorrelated for simplicity.
For the radial velocity of VFTS682 and of the 30 Doradus
region as a whole, we instead use the VFTS data
as quoted in \cite{bestenlehner:11}. \Tabref{tab:vfts682} lists the values adopted throughout
this work for each of these quantities.

@@

The red arrow in \Figref{fig:main} shows the direction of relative proper motion of
VFTS682 from \emph{Gaia} DR2 (see \Eqref{eq:pm_gaia_around}), and the
green arrows illustrate the uncertainty. % show the possible
% range of directions within the uncertainties in the measured relative proper
% motion.
These arrows cross at the present-day location of VFTS682 and
are prolonged in the direction opposite to the motion to illustrate
the possible range of origins. % The green arrow shows the direction of
% the relative proper motion from HST (see \Eqref{eq:pm_around_HST}),
% but we omit to show the possible range of directions from HST data, since it is
% insufficiently constrained to be useful.

@@

\begin{figure}%[tbp]
  \centering
  \includegraphics[width=0.48\textwidth]{./figures/main_plot_good_gaia_only}  
  \caption{The red solid arrow indicates the proper motion of VFTS682
    relative to the region from \emph{Gaia} DR2, starting from the present day position of
    the star. The green arrows indicate the possible
    directions of projected motion within the \emph{Gaia} DR2 errors, and are extended
    backwards (dashed) to illustrate the uncertainty on the origin of the
    star. The length of the prolongations is proportional to the relative proper motion
    times the kinetic age of VFTS682. % \todo{load color picture on background? Fig with HST data
      % available, but confusing...}
  }
